Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-11 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

We may need to understand how to define expectation values of an observable
for quantum IVPMs. Recall an observable is the quantum version of
a random variable. Hence, in order to define expectation values of
an observable, we need to understand the definition of expectation
values of a random variable for an classical IVPM. Since the expectation
value of random variable~$X$ is the integral $\int X\rmd\pmeas$~\cite{Kolmogorov1950},
we need to understand the meaning of integration on IVPMs. In the
rest of the section, we will consider the real-valued and interval-valued
probability measure defined in example~\ref{ex1} and \ref{ex3},
and see how to compute the expectation value of different random variables.

Consider the random variable~$X_{0}$ representing the number of
tails. For the probability measure~$\pmeas$ in example~\ref{ex1},
the expectation value of $X_{0}$ is
\begin{eqnarray*}
\int X_{0}\rmd\pmeas & = & 0\cdot\pmeas(\{HH\})+1\cdot\pmeas(\{HT,TH\})+2\cdot\pmeas(\{TT\})\\
 & = & 0\cdot\frac{1}{3}+1\cdot\frac{2}{3}+2\cdot0=\frac{2}{3}\textrm{ .}
\end{eqnarray*}

Now consider the IVPM~$\bar{\mu}$ in example~\ref{ex3}. First,
the only source use the exact same definition as ours is written by
Jamison and Lodwick~\cite{JamisonLodwick2004}. They introduced a
definition of integration as follow\footnote{\yutsung{Although they said they would explore their integration
in more details, they change their definition of IVPM later. Hence,
I don't know if they have any further development of their integration.}}. If we denote the indicator function by 
\begin{equation} 
\mathbf{1}_{A}(x)=\cases{ 
1 & if $x\in A$ ;\\ 
0 & if $x\notin A$, 
}
\end{equation}
then given a random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{A_{i}}$,
where $x_{i}$ are all different, the integral of $X$ is defined
by 
\begin{eqnarray*}
\int_{A}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)},\right.\\
 &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)}\right]\textrm{ .}
\end{eqnarray*}
For example, $X_{0}=0\cdot\mathbf{1}_{\{HH\}}+1\cdot\mathbf{1}_{\{HT,TH\}}+2\cdot\mathbf{1}_{\{TT\}}$,
and $\bar{\mu}\left(\Omega\right)=\left[1,1\right]$. Therefore, 
\begin{eqnarray*}
\int_{\Omega}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1},\right.\\
 &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1}\right]\\
 & = & \left[\inf\set{a_{1}+2a_{2}}{a_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ and }a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{0}+a_{1}+a_{2}=1},\right.\\
 &  & \left.\sup\set{a_{1}+2a_{2}}{a_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ and }a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{0}+a_{1}+a_{2}=1}\right]\\
 & = & \left[\inf\set{a_{1}+2a_{2}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{0}+a_{1}+a_{2}=1},\right.\\
 &  & \left.\sup\set{a_{1}+2a_{2}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{0}+a_{1}+a_{2}=1}\right]\\
 & = & \left[\inf\set{a_{1}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{0}+a_{1}=1},\right.\\
 &  & \left.\sup\set{a_{1}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{0}+a_{1}=1}\right]\\
 & = & \left[\frac{1}{2},1\right]
\end{eqnarray*}
What does this means...?

>>>>

We may need to understand how to define expectation values of an observable
for quantum IVPMs. Recall an observable is the quantum version of
a random variable. Hence, in order to define expectation values of
an observable, we need to understand the definition of expectation
values of a random variable for an classical IVPM. Since the expectation
value of random variable~$X$ is the integral $\int X\rmd\pmeas$~\cite{Kolmogorov1950},
we need to understand the meaning of integration on IVPMs. In the
rest of the section, we will consider the real-valued and interval-valued
probability measure defined in example~\ref{ex1} and \ref{ex3},
and see how to compute the expectation value of different random variables.
To simplify the discussion later, we will only consider a random variable~$X:\Omega\rightarrow\left[0,1\right]$
which is a step function, i.e., $X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{A_{i}}$,
where $A_{i}\in\events$ and $\mathbf{1}_{A}$ is the indicator function
defined by 
\begin{equation} 
\mathbf{1}_{A}(x)=\cases{ 
1 & if $x\in A$ ;\\ 
0 & if $x\notin A$. 
}
\end{equation}

Given a random variable~$X$ and a probability measure~$\pmeas$,
the expectation value of $X$ is 
\begin{eqnarray*}
\int X\rmd\pmeas & = & \sum_{i=1}^{N}x_{i}\pmeas\left(A_{i}\right)\textrm{ .}
\end{eqnarray*}
Intuitively, the expectation value is weighted average of the possible
outcomes of $X$ with the weight equal to the probability of each
outcome could happen. For example, consider the random variable~$X_{0}$
representing the number of tails. For the probability measure~$\pmeas$
in example~\ref{ex1}, the expectation value of $X_{0}$ is
\begin{eqnarray*}
\int X_{0}\rmd\pmeas & = & 0\cdot\pmeas(\{HH\})+1\cdot\pmeas(\{HT,TH\})+2\cdot\pmeas(\{TT\})\\
 & = & 0\cdot\frac{1}{3}+1\cdot\frac{2}{3}+2\cdot0=\frac{2}{3}\textrm{ .}
\end{eqnarray*}

After we discussed the conventional expectation value, we can start
to discuss the expectation value of IVPM. First, the only source use
the exact same definition as ours is written by Jamison and Lodwick~\cite{JamisonLodwick2004}
so it's reasonable to start from their definition of integration\footnote{Although they said they would explore their integration in more details,
they change their definition of IVPM later. Hence, I don't know if
they have any further development of their integration.}. Their integral of $X$ is defined by 
\begin{eqnarray*}
\int_{A}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)},\right.\\
 &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)}\right]\textrm{ .}
\end{eqnarray*}
In this definition, we still work on the weighted average. Since we
don't know the exact probability, we want to average on all possible
allowed probability, which represents the requirement on $a_{i}\in\bar{\mu}\left(A_{i}\right)$.
However, I don't have a clear intuition on why they want $\sum_{i=1}^{N}a_{i}=\min\bar{\mu}\left(A\right)$
and $\sum_{i=1}^{N}a_{i}=\max\bar{\mu}\left(A\right)$, and we will
have a more intuitive definition following this line when we move
on to Choquet integral.

After we have the definition, we can consider the IVPM~$\bar{\mu}$
in example~\ref{ex3} as an example. Because $\bar{\mu}\left(\Omega\right)=\left[1,1\right]$,
we have 
\begin{eqnarray*}
\int_{\Omega}X\rmd\bar{\mu} & = & \left[\inf\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1},\right.\\
 &  & \left.\sup\set{\sum_{i=1}^{N}x_{i}a_{i}}{a_{i}\in\bar{\mu}\left(A_{i}\right)\textrm{ and }\sum_{i=1}^{N}a_{i}=1}\right]\\
 & = & \left[\inf\set{a_{1}+2a_{2}}{a_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ and }a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{0}+a_{1}+a_{2}=1},\right.\\
 &  & \left.\sup\set{a_{1}+2a_{2}}{a_{0}\in\bar{\mu}\left(\{HH\}\right)\textrm{ and }a_{1}\in\bar{\mu}\left(\{HT,TH\}\right)\textrm{ and }a_{2}\in\bar{\mu}\left(\{TT\}\right)\textrm{ and }a_{0}+a_{1}+a_{2}=1}\right]\\
 & = & \left[\inf\set{a_{1}+2a_{2}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{0}+a_{1}+a_{2}=1},\right.\\
 &  & \left.\sup\set{a_{1}+2a_{2}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{2}=0\textrm{ and }a_{0}+a_{1}+a_{2}=1}\right]\\
 & = & \left[\inf\set{a_{1}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{0}+a_{1}=1},\right.\\
 &  & \left.\sup\set{a_{1}}{0\le a_{0}\le\frac{1}{2}\textrm{ and }\frac{1}{2}\le a_{1}\le1\textrm{ and }a_{0}+a_{1}=1}\right]\\
 & = & \left[\frac{1}{2},1\right]
\end{eqnarray*}
What does this means...?
